---
title: "701Project"
author: "Victoria Kalinovich"
date: "3/3/2020"
output:
  pdf_document: default
  html_document: default
---

## Final Analysis 


```{r}
library(dplyr)
test_project_id = read_csv("test.csv")

predictions = read_csv("final_test_preds.csv", col_names = FALSE)
predictions$index = test$X1
test_project_id$prediction = predictions$X1

test_project_id = test_project_id[,] 

head(test_project_id[order(test_project_id$prediction),c("title", "projectid", "teacher_gender", "high_poverty", "prediction")])

test_project_id 

```

```{r setup, include=FALSE}
library(tidyverse)

#outcomes = read_csv("outcomes.csv")
#project = read_csv("projects.csv")

#head(project)
#head(outcomes)
```


```{r}
#nrow(outcomes)
#nrow(project)

#merged = merge(project, outcomes, by = "projectid", all = TRUE)
#nrow(merged)

#test = merged[which(is.na(merged$fully_funded)),]
#train = merged[which(!is.na(merged$fully_funded)),]

#nrow(test)
#nrow(train)

#head(train)
```



```{r}
library(tidyverse)
library(caret)


valid = read_csv("full_valid.csv")

coeffs = read_csv("coefficents.csv")


valid_y = read_csv("y_valid.csv", col_names = FALSE)
valid_pred = read_csv("y_valid_pred.csv", col_names = FALSE)

labels = colnames(train)[2:(length(colnames(train))-3)]
train = read_csv("full_train.csv")
madhurir_315_theme <- theme_minimal() + theme(text = element_text(size = 14, color = "darkred"),  axis.text = element_text(size = 12, color = "darkblue"))


valid$y = valid_y$X1
valid$y_hat = valid_pred$X1
# num_ff = sum(train$y)
# num_nf = sum(train$y == 0)

# num_ff / (num_nf + num_ff)
# train$y_logreg = train_y$fully_funded

# train$y_logreg

# table(train$high_poverty,train$y)
```

```{r}
high_pov = sum(which(train$high_poverty > 0))
not_high_pov = sum(which(train$high_poverty < 0))
cat("Number of high poverty projects:", high_pov, "\n")
cat("Number of low poverty projects:",not_high_pov, "\n")
cat("Number of high poverty projects - low poverty:",high_pov - not_high_pov, "\n")

high_pov_val = sum(which(valid$high_poverty > 0))
not_high_pov_val = sum(which(valid$high_poverty < 0))



cat("Total Number of high poverty projects:", high_pov + high_pov_val, "\n")
cat("Number of low poverty projects:",not_high_pov + not_high_pov_val, "\n")
cat("Number of high poverty projects - low poverty:",(high_pov + high_pov_val) - (not_high_pov + not_high_pov_val), "\n")




female = sum(which(train$teacher_gender > 0))
male = sum(which(train$teacher_gender < 0))
cat("Number of projects with female teachers:", female, "\n")
cat("Number of male teacher projects:", male , "\n")
cat("Number of male minus female proejcts: ", female - male)

```


## Train Overall confusion matrix
```{r}
conf_mat_train = confusionMatrix(factor(train$y), factor(train$y_hat))$table
conf_mat_train
FP = conf_mat_train[2,1]
TN = conf_mat_train[1,1]

TP = conf_mat_train[2,2]
FN = conf_mat_train[1,2]

FPR = FP / (FP + TN)
cat("FPR:", FPR, "\n")
cat("accuracy:", (TP + TN) / (TP + TN + FN + FP))


```

## Validation Overall confusion matrix
```{r}
conf_mat = confusionMatrix(factor(valid$y), factor(valid$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]

TP = conf_mat[2,2]
FN = conf_mat[1,2]

FPR = FP / (FP + TN)
cat("FPR:", FPR, "\n")
cat("error:", (FP + FN) / (TP + TN + FN + FP))


```

```{r}
confusionMatrix(factor(valid$y), factor(valid$y_hat))


```

## Teacher Gender Confusion Matrix 

```{r}
## Female or gender = 0
train_f = train[which(train$teacher_gender < 0),]
conf_mat = confusionMatrix(factor(train_f$y), factor(train_f$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]

FPR = FP / (FP + TN)
print(FPR)
rm(train_f)
```


```{r}
## Male or gender = 1
train_m = train[which(train$teacher_gender > 0),]
conf_mat = confusionMatrix(factor(train_m$y), factor(train_m$y_hat))$table

FP = conf_mat[2,1]
TN = conf_mat[1,1]

FPR = FP / (FP + TN)
print(FPR)
rm(train_m)
```


## Urban / Rural / Suburban

```{r}
## rural
train_rural = train[which(train$school_metro_rural > 0),]
conf_mat = confusionMatrix(factor(train_rural$y), factor(train_rural$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]

FPR = FP / (FP + TN)
print(FPR)
rm(train_rural)
```

```{r}
## urban
train_urban = train[which(train$school_metro_urban > 0),]
conf_mat = confusionMatrix(factor(train_urban$y), factor(train_urban$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]

FPR = FP / (FP + TN)
print(FPR)
rm(train_urban)
```

```{r}
## suburban
train_suburban = train[which(train$school_metro_suburban > 0),]
conf_mat = confusionMatrix(factor(train_suburban$y), factor(train_suburban$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]

FPR = FP / (FP + TN)
print(FPR)

```

## Teacher Gender Confusion Matrix Train

```{r}
## Female or gender = 0
train_f = train[which(train$teacher_gender == 0),]
conf_mat = confusionMatrix(factor(train_f$y), factor(train_f$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]

FPR = FP / (FP + TN)
print(FPR)

```


```{r}
## Male or gender = 1
train_m = train[which(train$teacher_gender == 1),]
conf_mat = confusionMatrix(factor(train_m$y), factor(train_m$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]

FPR = FP / (FP + TN)
print(FPR)

```


## Teacher Gender Confusion Matrix Valid

```{r}
## Female or gender = 0
train_f_val = valid[which(valid$teacher_gender >  0),]
conf_mat = confusionMatrix(factor(train_f_val$y), factor(train_f_val$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]

FPR = FP / (FP + TN)
print(FPR)

```


```{r}
## Male or gender = 1
train_m_val = valid[which(valid$teacher_gender < 0),]
conf_mat = confusionMatrix(factor(train_m_val$y), factor(train_m_val$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]

FPR = FP / (FP + TN)
print(FPR)

```







## Train Poverty Level 

```{r}
## high pov
train_high = train[which(train$high_poverty > 0),]
conf_mat = confusionMatrix(factor(train_high$y), 
                           factor(train_high$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]

FPR = FP / (FP + TN)
print(FPR)

```

```{r}
## not high pov
train_nothigh = train[which(train$high_poverty < 0),]
conf_mat = confusionMatrix(factor(train_nothigh$y), 
                           factor(train_nothigh$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]

FPR = FP / (FP + TN)
print(FPR)

```


## Valid Poverty Level 

```{r}
## high pov
valid_high = valid[which(valid$high_poverty > 0),]
conf_mat = confusionMatrix(factor(valid_high$y), 
                           factor(valid_high$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]

TP = conf_mat[2,2]
FN = conf_mat[1,2]

FPR = FP / (FP + TN)
cat("FPR:", FPR, "\n")
cat("accuracty:", (TP + TN) / (TP + TN + FN + FP))


```

```{r}
## not high pov
valid_nothigh = valid[which(valid$high_poverty < 0),]
conf_mat = confusionMatrix(factor(valid_nothigh$y), 
                           factor(valid_nothigh$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]


TP = conf_mat[2,2]
FN = conf_mat[1,2]

FPR = FP / (FP + TN)
cat("FPR:", FPR, "\n")
cat("error:", (FP + FN) / (TP + TN + FN + FP))


```


# Neural Net Analysis 

```{r}
library(tidyverse)
library(caret)
# train_y = read_csv("train_y.csv")
# valid_y = read_csv("y_valid.csv")

# train_nn = read_csv("full_train_nn.csv")
valid_nn = read_csv("full_valid_nn_SMOTE_ESSAY.csv")

# train_nn_y = read_csv("nn_y_train_smote.csv", col_names = FALSE)
valid_nn_y = read_csv("nn_y_valid_SMOTE_ESSAY.csv", col_names = FALSE)

nn_pred_valid = read_csv("nnpred_valid_NEWLOSS_SMOTE.csv", col_names = FALSE)
# nn_pred_train = read_csv("nnpred_train1.csv", col_names = FALSE)

# train_nn$y = train_nn_y$X1
valid_nn$y = valid_nn_y$X1




# train_nn$y_hat = ifelse(nn_pred_train$X1 > .5, 1, 0)
valid_nn$y_hat = ifelse(nn_pred_valid$X1 > .5, 1, 0)




```


## Validation Overall confusion matrix
```{r}
conf_mat = confusionMatrix(factor(valid_nn$y), factor(valid_nn$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]

TP = conf_mat[2,2]
FN = conf_mat[1,2]

FPR = FP / (FP + TN)
cat("FPR:", FPR, "\n")
cat("error:", (FP + FN) / (TP + TN + FN + FP))

nrow(valid_nn)
conf_mat
```
```{r}
24751/ nrow(valid_nn)

```

## Valid Poverty Level 

```{r}
## high pov
valid_high_nn = valid_nn[which(valid_nn$high_poverty > 0),]
conf_mat = confusionMatrix(factor(valid_high_nn$y), 
                           factor(valid_high_nn$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]

TP = conf_mat[2,2]
FN = conf_mat[1,2]

FPR = FP / (FP + TN)
cat("FPR:", FPR, "\n")
cat("error:", (FP + FN) / (TP + TN + FN + FP))


```

```{r}
## not high pov
valid_nothigh_nn = valid_nn[which(valid_nn$high_poverty < 0),]
conf_mat = confusionMatrix(factor(valid_nothigh_nn$y), 
                           factor(valid_nothigh_nn$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]


TP = conf_mat[2,2]
FN = conf_mat[1,2]

FPR = FP / (FP + TN)
cat("FPR:", FPR, "\n")
cat("error:", (FP + FN) / (TP + TN + FN + FP))


```



## Teacher Gender Confusion Matrix Valid

```{r}
## Female or gender = 0
train_f_val_nn = valid_nn[which(valid_nn$teacher_gender >  0),]
conf_mat = confusionMatrix(factor(train_f_val_nn$y), factor(train_f_val_nn$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]

FPR = FP / (FP + TN)
print(FPR)
cat("error:", (FP + FN) / (TP + TN + FN + FP))

```


```{r}
## Male or gender = 1
train_m_val_nn = valid_nn[which(valid_nn$teacher_gender < 0),]
conf_mat = confusionMatrix(factor(train_m_val_nn$y), factor(train_m_val_nn$y_hat))$table
conf_mat
FP = conf_mat[2,1]
TN = conf_mat[1,1]

FPR = FP / (FP + TN)
print(FPR)
cat("error:", (FP + FN) / (TP + TN + FN + FP))
```


# CNN Analysis

```{r}
library(tidyverse)
cnn_valid = read_csv("validX.csv", col_names = FALSE)
head(cnn_valid)
ncol(cnn_valid)
```